Capitalized Title Here

### 2021-03-04 CMPSpaper_writing/CMPSpaper_writing.Rmd

---
title: Capitalized Title Here
header-includes:
  - \usepackage{xcolor}
  - \usepackage{longtable}
author:
  # see ?rjournal_article for more information
  - name: Author One
    affiliation: Affiliation
    address:
    - line 1
    - line 2
    url: https://journal.r-project.org
    orcid: 0000-0002-9079-593X
    email:  author1@work
  - name: Author Two
    url: https://journal.r-project.org
    email: author2@work
    orcid: 0000-0002-9079-593X
    affiliation: Affiliation 1
    address:
    - line 1 affiliation 1
    - line 2 affiliation 1
    affiliation2: Affiliation 2
    address2:
    - line 1 affiliation 2
    - line 2 affiliation 2
abstract: >
  An abstract of less than 150 words.
preamble: |
  % Any extra LaTeX you need in the preamble

>>>>

---
title: Capitalized Title Here
header-includes:
  - \usepackage{xcolor}
  - \usepackage{longtable}
author:
  # see ?rjournal_article for more information
  - name: Author One
    affiliation: ISU, CSAFE
    address:
    - line 1
    - line 2
    url: https://journal.r-project.org
    orcid: 0000-0002-9079-593X
    email:  author1@work
  - name: Heike Hofmann
    url: https://journal.r-project.org
    email: hofmann@iastate.edu
    orcid: 0000-0002-9079-593X
    affiliation: ISU, CSAFE
    address:
    - line 1 affiliation 1
    - line 2 affiliation 1
    affiliation2: Affiliation 2
    address2:
    - line 1 affiliation 2
    - line 2 affiliation 2
abstract: >
  An abstract of less than 150 words.
preamble: |
  % Any extra LaTeX you need in the preamble
